Tutorial_1

### 2024-07-23 Tutorial_1_descriptive_stats/Tutorial_1.Rmd
correct row0 info

# Read in the raw data from Panis and Schmidt (2016).

@@

# Do some wrangling to get a simpler data set.

@@

# create a row for time point 0
row0 <- c(bin=0,risk_set=riskset,events=0,hazard=0,se_haz=0,survival=1,se_surv=0,ca=NA,se_ca=NA)
# add new row
lifetable_blank_s6_complete <- lifetable_blank_s6 %>%
                                 add_row(!!! row0) %>%
                                 arrange(bin)
lifetable_blank_s6_complete
```

>>>>

# Read in the raw data from Panis and Schmidt (2016) - can be skipped.

@@

# Do some wrangling to get a simpler data set - can be skipped.

@@

# create a row for time point 0
row0 <- c(bin=0,risk_set=riskset,events=NA,hazard=NA,se_haz=NA,survival=1,se_surv=0,ca=NA,se_ca=NA)
# add new row
lifetable_blank_s6_complete <- lifetable_blank_s6 %>%
                                 add_row(!!! row0) %>%
                                 arrange(bin)
lifetable_blank_s6_complete
```
